Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2024-02-12 paper.tex
Fix formatting

The number of possible descriptors to quantify spatial structure developed
within different disciplines is stunning, for example: phase ratio or porosity
\cite{anovitz2015characterization}, surface area, radial distribution functions
\cite{zimm1948scattering,becker2010radial}, Minkowski functionals
\cite{vogel2010} and tensors \cite{schroder2011minkowski}, correlation functions
\cite{Torquato_book}, persistence diagrams
\cite{shivashankar2015felix,saadatfar2017pore,obayashi2018persistence}. The
evolution of such metrics was mainly induced by the ease of measurement and
interpretation. In fact, we need a single universal descriptor defined by only one characteristic -- information
content. The latter is an ability of the metric to describe the structure at
hand with 100$\%$ meaning the ability to fully recover the structure back from
this metric. Thus, universal descriptor has to possess following key properties:
(1) high information content, (2) ease of assess, (3) high compression ratio (i.e.,
descriptor is much "smaller" than the structure itself).

@@

\subsection{Analysis of anisotropic media}
When an analyzed sample is anisotropic, i.e., it is stretched or oriented along
some specific direction, it may be beneficial to align one of the cathetus of 
sampling triangle \cref{fig:pattern} with that direction. In this case the
anisotropy present in the sample will be properly captured by computed 3-pint correlation function.

>>>>

The number of possible descriptors to quantify spatial structure developed
within different disciplines is stunning, for example: phase ratio or porosity
\cite{anovitz2015characterization}, surface area, radial distribution functions
\cite{zimm1948scattering,becker2010radial}, Minkowski functionals
\cite{vogel2010} and tensors \cite{schroder2011minkowski}, correlation functions
\cite{Torquato_book}, persistence diagrams
\cite{shivashankar2015felix,saadatfar2017pore,obayashi2018persistence}. The
evolution of such metrics was mainly induced by the ease of measurement and
interpretation. In fact, we need a single universal descriptor defined by only
one characteristic -- information content. The latter is an ability of the
metric to describe the structure at hand with 100\% meaning the ability to
fully recover the structure back from this metric. Thus, universal descriptor
has to possess following key properties: (1) high information content, (2) ease
of assess, (3) high compression ratio (i.e., descriptor is much "smaller" than
the structure itself).

@@

\subsection{Analysis of anisotropic media}
When an analyzed sample is anisotropic, i.e., it is stretched or oriented along
some specific direction, it may be beneficial to align one of the cathetus of
sampling triangle \cref{fig:pattern} with that direction. In this case the
anisotropy present in the sample will be properly captured by computed 3-point
correlation function.
